### 2023-05-26 resilience.tex
sections
up

@@

\begin{example}
% Avec Safe = up( q_1(3,0) ) et Bad = q_0 (N,N) on aurait la 1-résilience et donc la résilience par exemple
% mais avec Safe = up(q_0(3,0)) et Bad = q_1(N,N) on ne l'aurait pas à cause de q_1(0,0) 
Let $V = (\{q_0,q_1\}, \{ (q_0, (3,0), q_1), (q_1, (-1,1), q_0)\})$ be a vector addition system with states (VASS),
and thus a WSTS (see Figure~1).
In the case $\Safe = \uparrow q_1(3,0)$ and $\Bad = \uparrow q_0(0,0)$, $1$-resilience holds.
On the other hand in the case $\Safe = \uparrow q_0(3,0)$ and $\Bad = \uparrow q_1(0,0)$, resilience does not hold because of $q_1(0,0) \in \Bad$.
% (si on veut se rajouter une hypothèse comme pas de dead-end on peut rajouter un troisième état q_2 duquel on puisse partir depuis q_1 en faisant par exemple +1,+1 et qui loop sur lui-même) 
\end{example}

\begin{center}
	\begin{figure}
			\hspace{3.75cm}
				\label{example_1}
\includegraphics[width=0.2\textwidth]{FigureA}
	\caption{}
	\end{figure}
\end{center}

\begin{example}
% Si on prends un Z-vass avec même seulement un compteur, Safe les entiers positifs, Bad le reste, avec juste une transition qui fait +1, alors on a la résilience (on reviens toujours dans les positifs) mais pas la bounded resilience.
Let us consider now a $\mathds{Z}$-VASS with only one state $q$, one counter, and one transition that adds $+1$ to the counter, with $\Safe = \uparrow q(0)$, $\Bad = \downarrow q(-1)$,
then resilience hold (one always ends up in the positive integers) but not bounded resilience: for every bound $b$ there is an element of $\Bad$ e.g. $q(-b-1)$ which necessitate at least $b+1$ steps before it can reach $\Safe$. 
\end{example}

>>>>

\alain{faire le lien avec home space, et les formules dans Schnoebelen}

@@

\begin{example}
Let us consider a $\mathds{Z}$-VASS with only one state $q$, one counter, and one transition that adds $+1$ to the counter, with $\Safe = \uparrow q(0)$, $\Bad = \downarrow q(-1)$,
then resilience hold (one always ends up in the positive integers) but not bounded resilience: for every bound $b$ there is an element of $\Bad$ e.g. $q(-b-1)$ which necessitate at least $b+1$ steps before it can reach $\Safe$. 
\end{example}
